---
title: "Buoy Project Report-Group 10"
author: "Chenghao Meng,Yinfeng Zhou and Feng Fan"
date: "2020/9/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1 Data Collection

To begin with,we need to collect data from the National Data Buoy Center (NDBC)-Station 4403.

```{r warning=FALSE}
library(tidyverse)

# Make URLs
url_1 = "http://www.ndbc.noaa.gov/view_text_file.php?filename=mlrf1h"
url_2 = ".txt.gz&dir=data/historical/stdmet/"

years = c(1987:2019)
urls = str_c(url_1, years, url_2, sep = "")
filenames = str_c("mr", years, sep = "")
```


```{r warning=FALSE}
n = length(years)
# Read the data on the website
for (i in 1:n){
   suppressMessages(  
    assign(filenames[i], read_table2(urls[i], col_names = TRUE)
  ))
}
```

### 1.1 Bind the Data from 1987-1999

```{r message=TRUE}
# Bind the data from 1987-1999

for (i in 1987:1998){
  if (i==1987)
    mr_pre<-mr1987
  else
    mr_pre = rbind(mr_pre,get(str_c("mr",i,sep = "")))
}
# Change the row name
names(mr_pre)[names(mr_pre) == "YY"] = "YYYY"

mr87_99 = rbind(mr_pre,mr1999)
if(mr87_99$YYYY<100){
    mr87_99$YYYY = mr87_99$YYYY + 1900
  }
head(mr87_99)
```

### 1.2 Bind the Data from 2000 to 2006

```{r}
for (i in 2000:2004){
    if (i==2000)
    mr00_06<-mr2000
    else
    mr00_06 = rbind(mr00_06,get(str_c("mr",i,sep = "")))
}
head(mr00_06)
```

```{r}
mr_pre_2 = rbind(mr2005,mr2006)
mr_pre_2 = subset(mr_pre_2, select = -c(mm))
mr00_06 = rbind(mr00_06,mr_pre_2)
tail(mr00_06)
```

### 1.3 Bind the Data from 2012 to 2019

```{r}
for (i in 2011:2019){
  if(i==2011)
    mr11_19<-mr2011
  else
    mr11_19 = rbind(mr11_19,get(str_c("mr",i,sep = "")))
}
names(mr11_19)[names(mr11_19) == "#YY"] = "YYYY"
mr11_19 = subset(mr11_19, select = -c(mm))
mr11_19 = mr11_19[-1,] # Delete the row with #YY etc.
head(mr11_19)
```

### 1.4 Bind the Data from 2007 to 2010

```{r}
mr_pre_3 = rbind(mr2007,mr2009)
mr_pre_4 = rbind(mr2008,mr2010)

mr07_10 = rbind(mr_pre_3,mr_pre_4)
names(mr07_10)[names(mr07_10) == "#YY"] = "YYYY"
mr07_10 = subset(mr07_10, select = -c(mm))
mr07_10 = mr07_10[-1,] # Delete the row with #YY etc.
head(mr07_10)
```

Now we conmapre the differences in column names between mr98_99 and mr00_06.

```{r}
colnames(mr87_99)
colnames(mr00_06)
```

We do some adjustments and bind them to get the data from 1987 to 2006.

```{r}
# Add TIDE to mr87_99
mr87_99$TIDE = c(rep(NA, times=nrow(mr87_99)))
# Check the colnames of mr_1
mr_1 = rbind(mr87_99,mr00_06)
colnames(mr_1)
```

### 1.5 Bind the Data from 2007 to 2019

```{r}
mr_2 = rbind(mr07_10,mr11_19)
colnames(mr_2)
```

```{r}
PRES = c(rep(NA, times=nrow(mr_1)))
mr_1 = cbind(mr_1[,1:11],PRES,mr_1[,12:ncol(mr_1)])
head(mr_1)
```

```{r}
BAR = c(rep(NA, times=nrow(mr_2)))
mr_2 = cbind(mr_2[,1:12],BAR,mr_2[,13:ncol(mr_2)])
names(mr_2)[names(mr_2) == "WDIR"] = "WD"
head(mr_2)
```

### 1.6 Get the Data from 1987 to 2019

So we bind mr_1 and mr_2 to get data from 1987-2019.

```{r}
mr = rbind(mr_1,mr_2)
head(mr)
```

```{r eval=FALSE}
# Download the file
write.table(mr,file="C:/Users/CH.Meng/Desktop/buoy.txt",row.names=FALSE,col.names=TRUE,sep = ",")
```

Now we finish the data collection.

## 2 Exploratory Data Analysis
### 2.1 Summary of the Dataset

Before making summary of the data, data type of certain columns should be transformed to numeric data.

```{r message=FALSE, warning=FALSE}
# Data type transformation
for (i in 5:ncol(mr))
  suppressMessages(
    mr[,i] <- as.numeric(mr[,i])
    )
```

Since "9999","999" and "99" in the dataset provide us with no specific information, we will replace those with NA.

```{r}
for (i in 1:ncol(mr))
  mr[,i][which(mr[,i]==9999|mr[,i]==999|mr[,i]==99)] = NA
```

Now we can have the summary of the dataset-mr, which will be transformed to tibble.
```{r}
# Summary of mr_tib
mr_tib = as_tibble(mr)
summary(mr_tib)
```

From the summary, we can see that there is no much variation in column WVHT, DPD, APD, MWD, DEWP, VIS and TIDE, and column PRES and BAR also contains a lot of NA's.

Since those columns cannot provide us with a lot of information, we will drop them for further analysis.

```{r}
# Drop the columns
mr_tib2 = mr_tib %>% 
  select(-WVHT, -DPD, -APD, -MWD, -DEWP, -VIS,
         -TIDE,-PRES,-BAR)
dim(mr_tib2)
```


```{r}
# Summary of mr_tib2
summary(mr_tib2)
```

### 2.2 Imputation of the Dataset

First, we will make histograms to explore the distribution of the columns.

#### 2.2.1 Histograms of the Columns
```{r}
# Hist. of WD
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WD),binwidth = 10)
```


```{r}
# Hist. of WSPD
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WSPD),binwidth = 0.5)
```


```{r}
# Hist. of GST
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=GST),binwidth = 0.5)
```


```{r}
# Hist. of ATMP
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=ATMP),binwidth = 0.5)
```


```{r}
# Hist. of WTMP
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WTMP),binwidth = 0.5)
```


#### 2.2.2 Conduct the Imputation 
According to the plots above, we will replace NA with median.

```{r}
mr_tib2[is.na(mr_tib2$WD),"WD"] =
  median(mr_tib2$WD,na.rm = T)

mr_tib2[is.na(mr_tib2$WSPD),"WSPD"] =
  median(mr_tib2$WSPD,na.rm = T)

mr_tib2[is.na(mr_tib2$GST),"GST"] =
  median(mr_tib2$GST,na.rm = T)

mr_tib2[is.na(mr_tib2$ATMP),"ATMP"] =
  median(mr_tib2$ATMP,na.rm = T)

mr_tib2[is.na(mr_tib2$WTMP),"WTMP"] =
  median(mr_tib2$WTMP,na.rm = T)
```

Then we will use the summary() to check if NA still existed.
```{r}
# Check the NA
summary(mr_tib2)
```
The summary indicates that no existed NA, the data can be used for further analysis.

### 2.3 Filter the Dataset

Make data type transformation on columns for Year, Month, Day and Hour. 

```{r message=FALSE}
for (i in 1:4)
  suppressMessages(
    mr_tib2[,i] <- as.integer(unlist(mr_tib2[,i]))
    )

# Solve the error caused by unknown reasons
mr_tib2$YYYY[which(mr_tib2$YYYY==3899)] = 1999
```


```{r message=FALSE}
# Load the packages
library(lubridate)
library(ggpubr)
```

Sort the dataset by quarter:
```{r}
mr_tib2['date']<-paste(mr_tib2$YYYY,mr_tib2$MM,mr_tib2$DD,mr_tib2$hh,sep="-")
mr_tib2['date']<-ymd_h(mr_tib2$date)
q1<-subset(mr_tib2,quarter(mr_tib2$date)==1)
q2<-subset(mr_tib2,quarter(mr_tib2$date)==2)
q3<-subset(mr_tib2,quarter(mr_tib2$date)==3)
q4<-subset(mr_tib2,quarter(mr_tib2$date)==4)
```

### 2.4 Explore the Pattern

#### 2.4.1 Air Temperature Pattern

Calculate each quarter's mean air temperature by year, and plot the patterns:
```{r message=FALSE}
# Quarter 1
meanq1<-aggregate(ATMP~YYYY,data=q1, mean)
q1reg<-ggplot(data = meanq1) + 
  geom_smooth(mapping = aes(x=YYYY,y=ATMP)) + 
  ggtitle("Average Air Temp. of Q1")

# Quarter 2
meanq2<-aggregate(ATMP~YYYY,data=q2, mean)
q2reg<-ggplot(data = meanq2) + 
  geom_smooth(mapping = aes(x=YYYY,y=ATMP)) + 
  ggtitle("Average Air Temp. of Q2")

# Quarter 3
q3reg<-meanq3<-aggregate(ATMP~YYYY,data=q3, mean)
q3reg<-ggplot(data = meanq3) + 
  geom_smooth(mapping = aes(x=YYYY,y=ATMP)) + 
  ggtitle("Average Air Temp. of Q3")

# Quarter 4
q4reg<-meanq4<-aggregate(ATMP~YYYY,data=q4, mean)
q4reg<-ggplot(data = meanq4) + 
  geom_smooth(mapping = aes(x=YYYY,y=ATMP)) + 
  ggtitle("Average Air Temp. of Q4")

# Put the plots together
ggarrange(q1reg,q2reg,q3reg,q4reg,ncol=2,nrow=2)
```

Sort the dataset by month, calculate each month's mean air temperature by year, and plot the patterns:
```{r message=FALSE}
mname<-str_c('m',1:12)
mmean<-str_c('meanm',1:12)
mreg<-str_c('m',1:12,'reg')

for(i in 1:12){
  assign(mname[i],subset(mr_tib2,month(mr_tib2$date)==i))
  assign(mmean[i],aggregate(ATMP~YYYY,data=get(mname[i]), mean))
  assign(mreg[i],(ggplot(data = get(mmean[i])) + 
  geom_smooth(mapping = aes(x=YYYY,y=ATMP)) + 
  ggtitle(paste("Average Air Temp. of M",i,sep=""))))
}
```

```{r message=FALSE}
# Put the plots together
ggarrange(m1reg,m2reg,m3reg,m4reg,ncol=2,nrow=2)
ggarrange(m5reg,m6reg,m7reg,m8reg,ncol=2,nrow=2)
ggarrange(m9reg,m10reg,m11reg,m12reg,ncol=2,nrow=2)
```

  From the plots listed above, it is shown that the average air temperature of each quarter in a year all increased throughout the past 30 years. Though by month the patterns are more variable, generally they all had an increasing tendency. 

#### 2.4.2 Water Temperature Pattern

Calculate each quarter's mean water temperature by year, and plot the patterns:
```{r message=FALSE}
# Quarter 1
meanq1_w<-aggregate(WTMP~YYYY,data=q1, mean)
q1reg_w<-ggplot(data = meanq1_w) + 
  geom_smooth(mapping = aes(x=YYYY,y=WTMP)) + 
  ggtitle("Average Water Temp. of Q1")

# Quarter 2
meanq2_w<-aggregate(WTMP~YYYY,data=q2, mean)
q2reg_w<-ggplot(data = meanq2_w) + 
  geom_smooth(mapping = aes(x=YYYY,y=WTMP)) + 
  ggtitle("Average Water Temp. of Q2")

# Quarter 3
meanq3_w<-aggregate(WTMP~YYYY,data=q3, mean)
q3reg_w<-ggplot(data = meanq3_w) + 
  geom_smooth(mapping = aes(x=YYYY,y=WTMP)) + 
  ggtitle("Average Water Temp. of Q3")

# Quarter 4
meanq4_w<-aggregate(WTMP~YYYY,data=q4, mean)
q4reg_w<-ggplot(data = meanq4_w) + 
  geom_smooth(mapping = aes(x=YYYY,y=WTMP)) + 
  ggtitle("Average Water Temp. of Q4")

# Put the plots together
ggarrange(q1reg_w,q2reg_w,q3reg_w,q4reg_w,ncol=2,nrow=2)
```

Sort the dataset by month, calculate each month's mean air temperature by year, and plot the patterns:
```{r}
mmean_w<-str_c('meanm_w',1:12)
mreg_w<-str_c('m',1:12,'reg_w')

for(i in 1:12){
  assign(mname[i],subset(mr_tib2,month(mr_tib2$date)==i))
  assign(mmean_w[i],aggregate(WTMP~YYYY,data=get(mname[i]), mean))
  assign(mreg_w[i],(ggplot(data = get(mmean_w[i])) + 
  geom_smooth(mapping = aes(x=YYYY,y=WTMP)) + 
  ggtitle(paste("Average Water Temp. of M",i,sep=""))))
}
```

```{r message=FALSE}
# Put the plots together
ggarrange(m1reg_w,m2reg_w,m3reg_w,m4reg_w,ncol=2,nrow=2)
ggarrange(m5reg_w,m6reg_w,m7reg_w,m8reg_w,ncol=2,nrow=2)
```

It is very interesting to look at the plot of water temperature. The average water temperature of Q3 is shown that there was a drastic decrease  since 2010, while compared to air temperature, there was a drastic increase in quarter 3 since 2010. 

However, in other quarters of the year, air temperature and water temperature didn't show a significant negative correlation. This might leads to further exploration in the variation of air temperature and the correlation with water temperature.

## 3 Model Analysis

Based on the result of pattern exploration in previous part, we are going to use linear model to fit the model between temperature and year.

### 3.1 Stationarity Test

First, we use ACF function to visualize the stationarity of the air and water temperature.
```{r}
# ACF of air temp.
par(mfrow=c(2,2))
acf(meanq1$ATMP,main="ACF-Air Temp. Q1")
acf(meanq2$ATMP,main="ACF-Air Temp. Q2")
acf(meanq3$ATMP,main="ACF-Air Temp. Q3")
acf(meanq4$ATMP,main="ACF-Air Temp. Q4")
```

From the ACF plots above, we can see that the pattern of air tmperature performs like white noise, so we can conclude that the time series of air temperature is stationary.

```{r}
# ACF of water temp.
par(mfrow=c(2,2))
acf(meanq1_w$WTMP,main="ACF-Water Temp. Q1")
acf(meanq2_w$WTMP,main="ACF-Water Temp. Q2")
acf(meanq3_w$WTMP,main="ACF-Water Temp. Q3")
acf(meanq4_w$WTMP,main="ACF-Water Temp. Q4")
```

From the ACF plots above, we can see that the pattern of water tmperature performs like white noise, so we can conclude that the time series of water temperature is stationary.

Then we can strat to bulid models on those two features.

### 3.2 Air Temperature
```{r}
# Fit the model of Air Temp.
air_q1 = lm(ATMP~YYYY,data = meanq1)
air_q2 = lm(ATMP~YYYY,data = meanq2)
air_q3 = lm(ATMP~YYYY,data = meanq3)
air_q4 = lm(ATMP~YYYY,data = meanq4)
```


```{r}
data.frame(Quarter=c("Q1","Q2","Q3","Q4"),
           Coef_AirTemp=c(air_q1$coefficients[2],
                          air_q2$coefficients[2],
                          air_q3$coefficients[2],
                          air_q4$coefficients[2])
           )

```

### 3.3 Water Temperature

```{r}
# Fit the model of Air Temp.
water_q1 = lm(WTMP~YYYY,data = meanq1_w)
water_q2 = lm(WTMP~YYYY,data = meanq2_w)
water_q3 = lm(WTMP~YYYY,data = meanq3_w)
water_q4 = lm(WTMP~YYYY,data = meanq4_w)
```

```{r}
data.frame(Quarter=c("Q1","Q2","Q3","Q4"),
           Coef_WaterTemp=c(water_q1$coefficients[2],
                          water_q2$coefficients[2],
                          water_q3$coefficients[2],
                          water_q4$coefficients[2])
           )
```

### 3.4 Conclusion and Limitations

From the plots shown above, the average air temperature over these 30 years did show an increasing tendency, no matter in quarterly scale or monthly scale. 

However, it seems that further information is still to be interpreted and explored, since we found out some interesting correlation between average water temperature and average air temperature. 

Also, the reason behind the variation of average air temperature is valuable to be digged in. 

## 4 Reference and Acknowledge

### 4.1 References

[1]Hadley Wickham, Romain François, Lionel Henry, Kirill Müller.(2020) dplyr: A Grammar of Data Manipulation, version 1.0.2

[2]Hadley Wickham.(2019) tidyverse: Easily Install and Load the 'Tidyverse', version 1.3.0

[3]Alboukadel Kassambara.(2020) ggpubr: 'ggplot2' Based Publication Ready Plots, version 0.4.0

[4]Tripti Dimri, Shamshad Ahmad and Mohammad Sharif. (2020) Time series analysis of climate variables using seasonal ARIMA approach. Journal of Earth System Science. 149 (2020) 

### 4.2 Acknowledgement

We sincerely thank Prof.Haviland for helping us to obtain open source data and provide guidance for our project. 