---
title: "Buoy Project"
author: "Chenghao Meng"
date: "2020/9/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1 Data Collection

To begin with,we need to collect data from the National Data Buoy Center (NDBC)-Station 4403.

```{r warning=FALSE}
library(tidyverse)

# Make URLs
url_1 = "http://www.ndbc.noaa.gov/view_text_file.php?filename=mlrf1h"
url_2 = ".txt.gz&dir=data/historical/stdmet/"

years = c(1987:2019)
urls = str_c(url_1, years, url_2, sep = "")
filenames = str_c("mr", years, sep = "")
```


```{r warning=FALSE}
n = length(years)
# Read the data on the website
for (i in 1:n){
   suppressMessages(  
    assign(filenames[i], read_table2(urls[i], col_names = TRUE)
  ))
}
```

## 1.1 Bind the data from 1987-1999

```{r}
# Bind the data from 1987-1999

for (i in 1988:1998)
  mr_pre = rbind(mr1987,get(str_c("mr",i,sep = "")))

# Change the row name
names(mr_pre)[names(mr_pre) == "YY"] = "YYYY"

mr87_99 = rbind(mr_pre,mr1999)
if(mr87_99$YYYY<100){
    mr87_99$YYYY = mr87_99$YYYY + 1900
  }
head(mr87_99)
```

## 1.2 Bind the data from 2000 to 2006

```{r}
for (i in 2001:2004)
  mr00_06 = rbind(mr2000,get(str_c("mr",i,sep = "")))

head(mr00_06)
```

```{r}
mr_pre_2 = rbind(mr2005,mr2006)
mr_pre_2 = subset(mr_pre_2, select = -c(mm))
mr00_06 = rbind(mr00_06,mr_pre_2)
tail(mr00_06)
```

## 1.3 Bind the data from 2012 to 2019

```{r}
for (i in 2012:2019)
  mr11_19 = rbind(mr2011,get(str_c("mr",i,sep = "")))

names(mr11_19)[names(mr11_19) == "#YY"] = "YYYY"
mr11_19 = subset(mr11_19, select = -c(mm))
mr11_19 = mr11_19[-1,] # Delete the row with #YY etc.
head(mr11_19)
```

## 1.4 Bind the data from 2007 to 2010

```{r}
mr_pre_3 = rbind(mr2007,mr2009)
mr_pre_4 = rbind(mr2008,mr2010)

mr07_10 = rbind(mr_pre_3,mr_pre_4)
names(mr07_10)[names(mr07_10) == "#YY"] = "YYYY"
mr07_10 = subset(mr07_10, select = -c(mm))
mr07_10 = mr07_10[-1,] # Delete the row with #YY etc.
head(mr07_10)
```

Now we conmapre the differences in column names between mr98_99 and mr00_06.

```{r}
colnames(mr87_99)
colnames(mr00_06)
```

We do some adjustments and bind them to get the data from 1987 to 2006.

```{r}
# Add TIDE to mr87_99
mr87_99$TIDE = c(rep(NA, times=nrow(mr87_99)))
# Check the colnames of mr_1
mr_1 = rbind(mr87_99,mr00_06)
colnames(mr_1)
```

## 1.5 Bind the data from 2007 to 2019

```{r}
mr_2 = rbind(mr07_10,mr11_19)
colnames(mr_2)
```

```{r}
PRES = c(rep(NA, times=nrow(mr_1)))
mr_1 = cbind(mr_1[,1:11],PRES,mr_1[,12:ncol(mr_1)])
head(mr_1)
```

```{r}
BAR = c(rep(NA, times=nrow(mr_2)))
mr_2 = cbind(mr_2[,1:12],BAR,mr_2[,13:ncol(mr_2)])
names(mr_2)[names(mr_2) == "WDIR"] = "WD"
head(mr_2)
```

## 1.6 Get the data from 1987 to 2019

So we bind mr_1 and mr_2 to get data from 1987-2019.

```{r}
mr = rbind(mr_1,mr_2)
head(mr)
```

```{r eval=FALSE}
# Download the file
write.table(mr,file="C:/Users/CH.Meng/Desktop/buoy.txt",row.names=FALSE,col.names=TRUE,sep = ",")
```

Now we finish the data collection.

# 2 Exploratory Data Analysis
## 2.1 Summary of the dataset

Before making summary of the data, data type of certain columns should be transformed to numeric data.

```{r}
# Data type transformation
for (i in 5:ncol(mr))
  suppressMessages(
    mr[,i] <- as.numeric(mr[,i])
    )
```

Since "9999","999" and "99" in the dataset provide us with no specific information, we will replace those with NA.

```{r}
for (i in 1:ncol(mr))
  mr[,i][which(mr[,i]==9999|mr[,i]==999|mr[,i]==99)] = NA
```

Now we can have the summary of the dataset-mr, which will be transformed to tibble.
```{r}
# Summary of mr_tib
mr_tib = as_tibble(mr)
summary(mr_tib)
```

From the summary, we can see that there is no much variation in column WVHT, DPD, APD, MWD, DEWP, VIS and TIDE, and column PRES and BAR also contains a lot of NA's.

Since those columns cannot provide us with a lot of information, we will drop them for further analysis.

```{r}
# Drop the columns
mr_tib2 = mr_tib %>% 
  select(-WVHT, -DPD, -APD, -MWD, -DEWP, -VIS,
         -TIDE,-PRES,-BAR)
dim(mr_tib2)
```


```{r}
# Summary of mr_tib2
summary(mr_tib2)
```

## 2.2 Imputation of the dataset

First, we will make histograms to explore the distribution of the columns.

### 2.2.1 Histograms of the columns
```{r}
# Hist. of WD
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WD),binwidth = 10)
```


```{r}
# Hist. of WSPD
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WSPD),binwidth = 0.5)
```


```{r}
# Hist. of GST
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=GST),binwidth = 0.5)
```


```{r}
# Hist. of ATMP
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=ATMP),binwidth = 0.5)
```


```{r}
# Hist. of WTMP
ggplot(data = mr_tib2) + 
  geom_histogram(mapping = aes(x=WTMP),binwidth = 0.5)
```


### 2.2.2 Conduct the imputation 
According to the plots above, we will replace NA with median.

```{r}
mr_tib2[is.na(mr_tib2$WD),"WD"] =
  median(mr_tib2$WD,na.rm = T)

mr_tib2[is.na(mr_tib2$WSPD),"WSPD"] =
  median(mr_tib2$WSPD,na.rm = T)

mr_tib2[is.na(mr_tib2$GST),"GST"] =
  median(mr_tib2$GST,na.rm = T)

mr_tib2[is.na(mr_tib2$ATMP),"ATMP"] =
  median(mr_tib2$ATMP,na.rm = T)

mr_tib2[is.na(mr_tib2$WTMP),"WTMP"] =
  median(mr_tib2$WTMP,na.rm = T)
```

Then we will use the summary() to check if NA still existed.
```{r}
# Check the NA
summary(mr_tib2)
```
The summary indicates that no existed NA, the data can be used for further analysis.

## 2.3 Filter the dataset

Make data type transformation to Year, Month, Day and Hour. 
```{r}

```

