---
title: "README"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Terminology Interpretion
APD: Average Period
ATMP: Air Temperature
BAR: Sea level pressure. (Now denoted as PRES.) 
DD: Day
DEWP: Dewpoint temperature taken at the same height as the air temperature measurement
DPD: Dominant wave period
hh: Hour
MM: Month
MWD: The direction from which the waves at the dominant period (DPD) are coming. The units are degrees from true North, increasing clockwise, with North as 0 (zero) degrees and East as 90 degrees.
VIS: Station visibility (nautical miles)
WD: Wind direction (the direction the wind is coming from in degrees clockwise from true N) during the same period used for WSPD. (Now denoted as WDIR)
WSPD: Wind speed (m/s) averaged over an eight-minute period for buoys and a two-minute period for land stations. 
GST: Peak 5 or 8 second gust speed (m/s) measured during the eight-minute or two-minute period. 
WTMP: Sea surface temperature (Celsius).  
WVHT: Significant wave height (meters) is calculated as the average of the highest one-third of all of the wave heights during the 20-minute sampling period. 


```{r}


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
